### 2012-11-25 paper.tex
added data in the tables

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree		&  0.846   	& 0.285   	& 0.843   & 0.846  &  0.844 		& FEHLT\\
  Random Forest		&  0.859   	& 0.333   	& 0.853   & 0.859  & 0.851     	& FEHLT\\
  Naive Bayes		 	&  0.83    	& 0.186   	& 0.854   & 0.83   & 0.837     	& FEHLT\\
  SVM							& 0.849    	& 0.343     &0.842   	&0.849   &0.842     	& 0.849\\
  kNN							&0.835     	&0.331      &0.829    &0.835   &0.831				& 0.835\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the adult dataset}
\end{table}

>>>>

The table below shos a comparison of the different algorithms on the adult dataset. For an algorithm we present here only the best obtained result concerning the TP rate. Values are always the weighted average.

@@

The table below shos a comparison of the different algorithms on the adult dataset. For an algorithm we present here only the best obtained result concerning the TP rate. Values are always the weighted average.

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   &  Correctly classified\\
	\midrule
	Decision Tree		& 0.86    	& 0.307   	& 0.854   & 0.86   & 0.855     & 		& FEHLT\\
  Random Forest		& 0.859   	& 0.333   	& 0.853   & 0.859  & 0.851     	& FEHLT\\
  Naive Bayes		 	& 0.83    	& 0.186   	& 0.854   & 0.83   & 0.837     	& FEHLT\\
  SVM							& 0.849    	& 0.343     &0.842   	&0.849   &0.842     	& 0.849\\
  kNN							&0.835     	&0.331      &0.829    &0.835   &0.831				& 0.835\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the adult dataset}
\end{table}
